Staged Abstract Interpreters

### 2019-03-27 paper/50_stageabs.tex
misc

As we can see, the @RepSetLattice@ is an instance of @RepLattice@, which is also
an abstraction of the manipulations on the foundamental data structure. For
staged versions, these operations eventually are delegated to the @subsetOf@,
@union@ and @intersect@ operation on @Rep[Set[T]]@. We even don't have to change
the implementation code, but just the types – from @Set[T]@ to @Rep[Set[T]]@. In
the code generation part, these operations emit their corresponding next-stage
code. Again, other lattice structures such as products and maps are implemented
in a similar way.

>>>>

As we can see, the @RepSetLattice@ is an instance of @RepLattice@, which is also
an abstraction of the underlying data structure. The lattice operations
eventually are delegated to @subsetOf@, @union@ and @intersect@ on
@Rep[Set[T]]@. We even don't have to change the implementation code, but just
the types – from @Set[T]@ to @Rep[Set[T]]@. LMS library provides an implicit
conversion lifting to next-stage values. In the code generation part, these
operations emit their corresponding next-stage code. Again, other lattice
structures such as products and maps are implemented in a similar way.
